Supplementary Materials

### 2021-02-04 analysis/analysis.Rmd
Figure 1 text wrap
changes some text about R2

We can see that although the correlation is relatively weak, our confidence interval indicates that we can be reasonably positive that $R^2>0$ (i.e, 95\% credible interval is `r round(bR2[3],2)` - `r round(bR2[4], 2)`).

>>>>

The confidence interval indicates that we can be confident that $R^2>0$ (i.e, 95\% credible interval is `r round(bR2[3],2)` - `r round(bR2[4], 2)`).
